An analysis of interrelations between economic and environmental variables in Australian Winegrowing.

### 2023-08-31 article.tex
its a title

%% \title{Title\tnoteref{label1}}
\title{???Grape Quality and its Link to Regional Differences in the Australian Winegrowing Industry}
% Regional differences in Australian winegrowing (Quality)?

@@

\begin{abstract}
\end{abstract}
%%Graphical abstract`
%\begin{graphicalabstract}
 % \includegraphics{graphical_abstract.jpeg}
%\end{graphicalabstract}'

@@

\if{false}

We classify regions to find the most prominent and well-defined relationships to regions.
We examine the variables that are the most decisive in determining region.
We compare the similarities and differences of these regions
- within the analysis and
- within the literature (also in their definition and history)

We examine the similarity between these classifications and the variables that are significant in classifying profitable vs not.
How do regional changes affect that. What is similar and what is different.

We can link these contributing factors back to the baselines - at least anecdotally, or in an unpublished section. This will be good for the thesis.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The Australian wine-growing industry is a rich and diverse landscape that is separated into multiple Geographical Indicator Regions. Each region describing unique reputations, qualities and varietals of wine produced there. While a great deal has been done regarding individual regional properties and traits, there has been little statistical insight into broader regional comparisons; due to a lack of cross-regional and in-depth data sources \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. In this study we use Classification Trees to compare regional differences and how these differences relate to sustainable practices. 
\newline

%
%This analysis addresses the knowledge gap regarding the effectiveness of regional level strategies employed in the wine industry and their relation to grape quality.
% What the hell is a regional strategy
% And how do you define, or know what trategy each region is using?
%
Through the use of classification trees this study aims to highlight the key differences in sustainable practices at a regional level and how these practices relate to the different grades of grape quality.

@@

\if{false}
\begin{figure}
  \includegraphics{violinplot.pdf}
  \caption{Violin plots of GI Region and Year coefficients for each model.}\label{fig:violin}
  \end{figure}
 %
\fi{}

>>>>

%% \title{Title\tnoteref{label1}}
\title{An analysis of interrelations between economic and environmental variables in Australian Winegrowing.}

% 
% Variable importance in determining vineyard operational costs and region using statistical machine learning.
% How are region and operational costs related?

% Regional differences in Australian winegrowing (Quality)?

@@

% \begin{abstract}
% \end{abstract}
%%Graphical abstract`
%\begin{graphicalabstract}
 % \includegraphics{graphical_abstract.jpeg}
%\end{graphicalabstract}'

@@

In the past decade, the Australian winegrowing industry has undergone a variety of pressures, such as changing market demands, disease and drought \citep{wineaustraliaAustralianWineProduction2021}. Furthermore, natural resources are likely to decrease, as pressures from climate change increase, making it more important than ever to improve the efficiency and sustainability of crops \citep{agdeeNationalGreenhouseAccounts2021}. It has become crucial for those in the wine industry to address issues relating to environmental sustainability and economic viability, with a growing need for the industry to close the research gaps between sustainable practices and their real and perceived environmental and economic advantages \citep{montalvo-falconSustainabilityResearchWine2023,ouvrardDoesSustainabilityPush2020}. This paper aims to provide a comprehensive analysis of the intricate relationships between economic and environmental variables within the winegrowing sector. By employing statistical machine learning we show how interconnected vineyard variables are. Utilising a ten year data set that spans Australia we show the predominant elements in classifying region and year, as well as determining a vineyards potential operational costs and profit.
\par
This analysis utilises XGBoosted trees to classify region and year; and to determine operating cost and profit of Australian vineyards. Classification and regression trees are utilised as surrogate models to shed insight into the key partitions used by the XGBoost ensembles. Variable importance is further used to illustrate the interconnectedness of the different predictor variables, and to show the similarity in variable importance between different response variables (particularly between region and operational cost). This study aims to assist in uncovering the complexity of variables that are affected by a variety of vineyard management decisions to illustrate complex interplay of variables. This study endeavours to gain insight into the similarity in predictor variable importance between year, region, operational costs and profit.

% Initiatives to improve the environmental impacts of the Australian Wine industry have been ongoing since the 1990s; with recommendations to implement strategies for national programs that would help educate industry members in sustainable practices (Keith Jones, 2002). The first legislative initiative to support national programs was the Environmental Management Guidelines for Vineyards in Western Australia during 2002 (Nind, 2002). The first national program was the Australian Wine Industry Stewardship, beginning shortly after, during 2004 (WFA, 2009). This program was replaced multiple times during the 2000s, first by the Australian Wine Environmental Stewardship, and then by EnviroWine, finally becoming EntWine in 2009. The period in the 2000s was further influenced by several key researchers and program leaders, where concurrently multiple regions developed approaches to sustainable management tied to sustainability programs (SWA, 2023). EntWine was eventually acquired by the Australian Wine Research Institute and Australian Grape & Wine during 2015; which would lead to its redevelopment into Sustainable Winegrowing Australia (SWA) during 2019/2020 (SWA, 2023).
%             2.1.2. Previous Research and Motivation
% During the period of 2010 to 2023 data was collected voluntarily from wine industry members through the national sustainability programs, ultimately being in SWA possession as of 2023. The data set was used in 2020 to analyse sustainable practices, resulting in the development of a Resource Intensity Score (RIS); where the RIS was a summary indicator value of a vineyard’s energy use, emissions and water use (Nayak et al., 2020). The analysis then fit vineyards’ RIS values to 55 variables sourced from 23 separate wine regions during the period of 2015 to 2018 through the use of Stepwise Regression modelling. It was found that the top 10% gross margin vineyards had a lower operating cost and a lower RIS score than vineyards in the bottom 10% gross margin.
% The motivation for this thesis is to investigate the differences between the top 10% gross margin vineyards and those of the bottom 10%, hoping to uncover what the key differences were and to relate them to sustainable practices; as there is a known gap in the literature due to the difficulty to evaluate relationships using empirical evidence of both the environmental and economic impacts of sustainable practices in viticulture. This difficulty stems from data scarcity, industry complexity and transparency. While there have been attempts to fill these gaps, methodologies and indicators have lacked in ability to compare different regions and scales (Baiano, 2021).
%             2.1.3. Economic Pressures
%             2.1.4. Environmental Pressures
% There are several environmental concerns that affect viticulture, including loss of soil quality, lack of rain, hail, disease, fire, and frost; with climate change exacerbating these issues. In 2020, 40,000 tonnes of grapes were lost across 18 different wine regions due to bush fires and smoke taint; the predicted incidence of wildfires is expected to increase (Canadell et al., 2021). In comparison to countrywide pressures such as drought, this damage made up only 3% of the total amount of grapes for that year; although acknowledged as a considerable loss on an individual basis, it was deemed to be only a minor national concern by Wine Australia when compared to other environmental pressures such as drought (Wine Australia, 2020).

% \if{false}

% We classify regions to find the most prominent and well-defined relationships to regions.
% We examine the variables that are the most decisive in determining region.
% We compare the similarities and differences of these regions
% - within the analysis and
% - within the literature (also in their definition and history)

% We examine the similarity between these classifications and the variables that are significant in classifying profitable vs not.
% How do regional changes affect that. What is similar and what is different.

% We can link these contributing factors back to the baselines - at least anecdotally, or in an unpublished section. This will be good for the thesis.

% \fi

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The Australian wine-growing industry is a rich and diverse landscape that is separated into multiple Geographical Indicator Regions. Each region describing unique reputations, qualities and varietals of wine produced there. While a great deal has been done regarding individual regional properties and traits, there has been little statistical insight into broader regional comparisons; due to a lack of cross-regional and in-depth data sources \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. In this study we use Classification Trees to compare regional differences and how these differences relate to sustainable practices. 
% \newline

%
%This analysis addresses the knowledge gap regarding the effectiveness of regional level strategies employed in the wine industry and their relation to grape quality.
% What the hell is a regional strategy
% And how do you define, or know what trategy each region is using?
%
% Through the use of classification trees this study aims to highlight the key differences in sustainable practices at a regional level and how these practices relate to the different grades of grape quality.

@@
